A finite-state morphological transducer for Kyrgyz

### 2012-03-12 paper/paper.tex
Some bib fixes

%FIXME: broken citation: "altinasi"? maybe altintas?
The project is designed based on the Helsinki Finite State Toolkit \citep{linden2011} which is a free/open-source reimplementation of the Xerox finite-state toolchain, popular in the field of morphological analysis. It implements both the \textbf{lexc} formalism for defining lexicons, and the \textbf{twol} and \textbf{xfst} formalisms for modeling morphophonological rules. It also supports other finite state transducer formalisms such as \textbf{sfst}. This toolkit has been chosen as it -- or the equivalent XFST -- has been widely used for other Turkic languages \citemultileft{coltekin2010}, \citemultimid{altinasi2001}, \citemultiright{tantug2006}, and is available under a free/open-source licence.

@@

\bibliographystyle{styler}
\bibliography{paper}

>>>>

The project is designed based on the Helsinki Finite State Toolkit \citep{linden2011} which is a free/open-source reimplementation of the Xerox finite-state toolchain, popular in the field of morphological analysis. It implements both the \textbf{lexc} formalism for defining lexicons, and the \textbf{twol} and \textbf{xfst} formalisms for modeling morphophonological rules. It also supports other finite state transducer formalisms such as \textbf{sfst}. This toolkit has been chosen as it -- or the equivalent XFST -- has been widely used for other Turkic languages \citemultileft{coltekin2010}, \citemultimid{altintas2001}, \citemultiright{tantug2006}, and is available under a free/open-source licence.

@@

\bibliographystyle{lrec2006}
\bibliography{paper}
